IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/retrofit.tex
simple
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Our general embedding approach provides these semantics by construction.
%
To show this, consider, first, the encoding of the sequential |toLabeled|
construct in our framework:
\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let i = taskId; | \\
    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
\end{align*}
When using the sequential scheduler |seqf|, the sandboxed task runs to
completion before returning to the task that sandboxed it. 
(Here, a task list can be interpreted as a number of information flow aware
stack frames.)
To read the result of a |toLabeled| operation
(which is communicated via message passing), the parent task must raise
its label; otherwise the label will get dropped, as per the \textsc{I-recv}
rule.\footnote{A keen reader may note that with a single, per-task channel, we
might mix up our messages.  Indeed, a proper development requires the ability
to allocate fresh channels; for purposes of simplicity, this has been omitted.}

Second, suppose that our |targetLangML| is extended with a single exception
expression |fail|, which reduces to |fail|, removing all containing |tE|
evaluation contexts, i.e., it propagates up to a |IT (-)| boundary.
%
In this setting, it is clear that exceptions cannot cross boundaries.
%
For instance, 
\begin{code}
TI(toLabeled l (IT (if te then fail else true))); true
\end{code}
always evaluates to |true|, regardless of the value of |te|.
%
As in both LIO and Breeze, however, only when calling |recv| on such messages
will the exception be propagated.
%
This of course, is not a leak since the current label must be raised before
receiving sensitive message, regardless of their content.

>>>>

Our general embedding approach provides these semantics by construction.
%
To show this, we first define an encoding of the sequential |toLabeled|
construct in our framework:
\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let i = taskId; | \\
    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
\end{align*}
When using the sequential scheduler |seqf|, the sandboxed task runs to
completion before returning to the task that sandboxed it. 
(Here, a task list can be interpreted as a number of information flow aware
stack frames.)
To read the result of a |toLabeled| operation
(which is communicated via message passing), the parent task must raise
its label; otherwise the label will get dropped, as per the \textsc{I-recv}
rule.\footnote{A keen reader may note that with a single, per-task channel, we
might mix up our messages.  Indeed, a proper development requires the ability
to allocate fresh channels; for purposes of simplicity, this has been omitted.}

Now suppose that our |targetLangML| is extended with a single exception
expression |fail|, which reduces to |fail|, removing all containing |tE|
evaluation contexts, i.e., it propagates up to a |IT (-)| boundary.
%
In this setting, it is clear that exceptions cannot cross boundaries.
%
For instance, 
\begin{code}
TI(toLabeled l (IT (if te then fail else true))); true
\end{code}
always evaluates to |true|, regardless of the value of |te|.
%
Just like in both LIO and Breeze, however, only when calling |recv| on such messages
will the exception be propagated.
%
This of course, is not a leak since the current label must be raised before
receiving sensitive message, regardless of their content.
